Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-27 sattose/paper.tex
Revert "Removed the survey"
This reverts commit 27a5c8017df0b8b10576add883881c3238896e57.

>>>>

\subsection{Survey on Clone Detection Tools}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview.
\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged. Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}

None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}. This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
